Appendix

### 2019-10-18 manuscript/appendix.Rmd
more detail on land-use fig

```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```

>>>>

```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops. For illustration in this example, only corn, soybeans, and pasture are shown. Rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```
